### 2016-03-09 paper/layered_depthmap.tex
yasu

\subsection{Swarm Fusion Layered Depthmap Estimation}

>>>>

\subsection{Swarm Fusion layered depthmap estimation}
Lastly, we will evaluate Swarm fusion on a very challenging layered
depthmap estimation problem~\cite{layered_depthmap}, which has been
recently proposed (see the anonymized pdf in the supplementary
material). The problem seeks to infer layered depthmap representation
from an RGBD image, where the challenge is the massive solution space,
which is exponential in the number of layers.~\footnote{Authors have
proposed a novel fusion scheme, where a solution subspace instead of a
single solution is generated by a proposal generation scheme in each
iteration. Since a solution subspace is eqivalent to multiple solution
proposals, their algorithm can be easily integrated into our swarm
fusion framework.  However, competing fusion methods (e.g., fusion move
or hierarchical fusion) cannot handle a solution subspace proposal,
making it impossible to conduct comparative evaluations. Therefore, we
choose to use a simple solution proposal instead of a subspace in our experiments.}

\mysubsubsection{Baseline methods}
The number of labels is extremely large (an order of 10,000 \yasu{what
were the number of labels in our cvpr16?}), which eliminates the
possibility of using hierarchical fusion. Therefore, we will evaluate
fusion move and parallel fusion move algorithm as in the case of optical
flow problem, where one solution proposal repeats being fused via QPBO.

\mysubsubsection{Swarm fusion implementation}
All the three swarm fusion methods are tested.

### 2016-03-09 paper/optical_flow.tex
yasu

We use Swarm fusion to solve an optical flow problem, where a baseline
is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
Although their paper did not consider parallel implementation, it is
straightfoward to apply the concept of parallel alpha-expansion and
construct a ``parallel fusion move'' method, where multiple threads
repeat fusing two solutions via QPBO. This time, we will compare it with
our full swarm fusion model (bottom right example in
Fig.~\ref{fig:model}).

>>>>

The second problem is an optical flow problem, where Lempitsky
introduced the fusion move algorithm~\cite{viktor}. We have used the
energy definitions and proposals generation schemes as described in the
paper. We again use test datasets from
Middlebury~\cite{middlebury_optical_flow}.

\mysubsubsection{Baseline methods} The first baseline is the FM
algorithm exactly as given in the paper.  Although their paper did not
consider parallel implementation, it is straightfoward to apply the
concept of parallel alpha-expansion. Therefore, the second baseline is
the ``parallel fusion move'' method (replacing constant label solutions
with proposals inside ``parallel alpha-expansion'' in
Fig.~\ref{fig:model}).

\mysubsubsection{Swarm fusion implementation}
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The full swarm fusion model (at the bottom right in
Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
method. We will also try the other two Swarm fusion variants in
Fig.~\ref{fig:model} with restrictions.

### 2016-03-09 paper/stereo.tex
yasu

\section{Swarm Fusion implementations}
We now explain detailed implementation of the Swarm Fusion method for
three problems in Computer Vision.

@@

\mysubsubsubsection{Baseline methods}

@@

\mysubsubsubsection{Swarm fusion implementation}

>>>>

\section{Swarm Fusion implementations} \yasu{this section is very rough
at the moment. requires polishing. but algorithms might change as we run
experiments.}
We now explain detailed implementation of the Swarm Fusion method for
three problems in Computer Vision.

@@

\mysubsubsection{Baseline methods}

@@

\mysubsubsection{Swarm fusion implementation}
